A Global Market for Marine Conservation

### 2021-04-14 draft.Rmd
Added very vry rough draft
pdated draft with random sentences

@@

>>>>

It is important that we acknowledge the equity concerns of any conservation intenrvention. Under the current approach to conservation, nations face two options: to conserve 30% in situ, or not engage in conservation at all. This market-based approach allows for a third option: it allows nations to decide how much to conserve in their waters.

Ocean grabbing, the term that relates to the loss of soveraignty in the ocean (see Benett) may be perceived as a problem. However, nations are not forced to conserve in situ, and will only do so if they are approrpiately compensated for it.

All ecosystems are euqlly important for the subsistance of nature and species that reside in them. But a coral reef is not comparable to a kelp forest.  A market design that doesn't acknowledge these differences may unintendendly bias conservation towards different ecosystems or geographic regions. When outcomes of a market are restricted to a geographic extent, such as air pollution markets, a buble policy is implemented. We borrow from this principle and use biogeographic regionalization principles to create ecologically-coherent market segments where nations trade similar habitat. For example, in the temperate eastern pacific, Mexico and the US will trade a same type of habitat, while in the Tropical Atlantic they wil.

Having tackled these three limitations (spatially-independent measure, x, and market bubbles), we proceed to simulate the trade outcomes of such a market. We evaluate the outcomes across a range of target coverages (1 - 100), and find that a market always results in reduced costs. The absolute and relative magnitude of the costs-savings changes with protection target, peaking at between X and Y, depending on of the choice market segmentation. Intuitively, increasing teh number of market segments reduces the opportunity for bargaining and reduces the gains from trade, but ensures the persistance of different habitats.

We pay especial attention to goals of interest, such as protecting 30% of the marine area (habitat suitability-weighted) within all national jurisdictions. We find that a market-based approach to conservation would reduce costs by X%, and that Y% less area would be needed.

@@

# Supplementary Information
